The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-12-03 paper/paper.qmd
update paper

confusion_df <- as.data.frame(as.table(confusion_matrix_tree$table))
kable(confusion_df, format = "markdown", col.names = c("Prediction", "Reference", "Freq"))

>>>>

confusion_df <- as.data.frame(as.table(confusion_matrix_tree$table))

confusion_df <- confusion_df %>%
  mutate(Prediction = gsub("_", " ", Prediction),
         Reference = gsub("_", " ", Reference))
kable(confusion_df, format = "markdown", col.names = c("Prediction", "Reference", "Freq"))
